Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2016-05-05 paper.tex
slowly adding packages without breaking stuff

\documentclass{sig-alternate-05-2015}
\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{17,686,161}

>>>>

\documentclass{sig-alternate-05-2015}

\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
\usepackage{color}
\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}

% for footnotes in tables
\usepackage{tablefootnote}

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\footnotesize,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{17,686,161}
